---
title: "Cohort 1 Coach Assignments"
output: github_document
---

```{r setup, include=FALSE}
  knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE,
                        cache = TRUE)
  options(scipen=999)
  library(tidyverse)
```

# Introduction

In Cohort 1, IPA randomly assigned coaches to format (individual/group) and then to groups assigned to the same format (individual: arms 1 and 3; group: arm 2). These assignments are spread across two files from Jan 10, 2019:

```{r}
  path <- "/Users/epg4/Box Sync/AVSI Coaching/AVSI Coaching (Duke IPA)/Design/Assignments/"
  
  ipa_host <- readxl::read_excel(paste0(path, "coach_gr25_long_host_10 Jan 2019_sortCoach.xls")) %>%
    mutate(setting = "Host")
  
  ipa_ref <- readxl::read_excel(paste0(path, "coach_gr25_long_ref_10 Jan 2019_sortCoach.xls")) %>%
    mutate(setting = "Refugee")
  
  ipa <- bind_rows(ipa_host, ipa_ref) %>%
    mutate(in_ipa = "yes") 
  
  ipa
```

After randomization, AVSI made some changes to coach assignments. This file came from AVSI's M&E team:

```{r}
  avsi <- readxl::read_excel(paste0(path, "Cohort one coach assignment.xlsx")) %>%
      rename("Setting" = "Participant Type") %>%
    mutate(in_avsi = "yes") %>%
    select(-`Coach Name`, -`Group Name`)
  
  avsi
```
# Number of coaches 

```{r}
  ipa %>%
    distinct(coachid, .keep_all = TRUE) %>%
    group_by(setting) %>% 
    count() %>% ungroup %>%
    mutate(N = sum(n))
```
```{r}
  avsi %>%
    distinct(`Coach ID`, .keep_all = TRUE) %>%
    group_by(Setting) %>% 
    count() %>% ungroup %>%
    mutate(N = sum(n))
```

# Matching coach IDs

```{r}
  ipa %>%
    distinct(coachid, .keep_all = TRUE) %>%
    rename("Village Cluster" = "vil_clus") %>%
    select(coachid, in_ipa, `Village Cluster`) %>%
    full_join(select(distinct(avsi, `Coach ID`, .keep_all=TRUE),
                     `Coach ID`, in_avsi, `Village Cluster`), 
              by = c("coachid" = "Coach ID")) %>%
    mutate(in_ipa = case_when(
      is.na(in_ipa) ~ "no",
      TRUE ~ in_ipa
    )) %>%
    mutate(in_avsi = case_when(
      is.na(in_avsi) ~ "no",
      TRUE ~ in_avsi
    )) %>%
   {. ->> combined} %>%
    group_by(in_ipa, in_avsi) %>% count()
```

# Number of groups per coach

IPA randomized group coaches to 5 groups.

```{r}
  ipa %>%
    group_by(grouptype, coachid) %>% count(name = "groups") %>% 
    group_by(grouptype, groups) %>% count(name = "coach count")
```

AVSI found that 5 groups was too much and added more coaches to reduce the group load to 3.

```{r}
  avsi %>%
    mutate(grouptype = case_when(
      `HH Arm` == "Arm 2" ~ "group",
      TRUE ~ "ind")) %>%
    group_by(grouptype, `Coach ID`) %>% count(name = "groups") %>% 
    group_by(grouptype, groups) %>% count(name = "coach count")
```

# Matching village cluster IDs

```{r}
  ipa %>%
    distinct(vil_clus, .keep_all = TRUE) %>%
    select(vil_clus, in_ipa) %>%
    full_join(select(distinct(avsi, `Village Cluster`, .keep_all=TRUE),
                     `Village Cluster`, in_avsi), 
              by = c("vil_clus" = "Village Cluster")) %>%
    mutate(in_ipa = case_when(
      is.na(in_ipa) ~ "no",
      TRUE ~ in_ipa
    )) %>%
    mutate(in_avsi = case_when(
      is.na(in_avsi) ~ "no",
      TRUE ~ in_avsi
    )) %>%
    group_by(in_ipa, in_avsi) %>% count()
```
# Matching coach assignments for coach IDs in both

```{r}
  combined %>%
    filter(in_ipa == "yes" & in_avsi == "yes") %>%
    mutate(same_vc = case_when(
      `Village Cluster.x` == `Village Cluster.y` ~ "yes",
      TRUE ~ "no"
    )) %>%
    group_by(same_vc) %>% count() %>%
    ungroup() %>% mutate(N = sum(n))
```

